PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
more missigness updates

@@

@@

@@

#GAD - baseline
GAD Missingness NAs per person - count and percentages
```{r gad baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
           %in%
             gad.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_base = 
      na_per_person_gad_base/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
```

#GAD - retrospective
GAD Missingness NAs per person - count and percentages
```{r gad retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
           %in%
             gad.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_retro = 
      na_per_person_gad_retro/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
```

#GAD - prepandemic
GAD Missingness NAs per person - count and percentages
```{r gad prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
           %in%
             gad.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_prepan = 
      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
```

Count for gad baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for gad}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
```

>>>>

## Missigness

## prepandemic
```{r PCL prepan missingness}
glad.pcl.raw.id <- glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_prepan])
      )
  )

glad.pcl.raw.id %>%
  freq(na_per_person_pcl_prepan,
       cumul = F)
```

@@

Missigness

baseline
```{r coping gad baseline missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_base])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
```

```{r coping gad retrospective missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(
        is.na(.[gad.items_retro])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
```

@@

PCL missingness (NAs per person)

baseline
```{r coping pcl baseline missingness}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_base =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_base])
      )
  )

coping.glad.pcl.raw.id %>%
  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
```

retrospective
```{r coping pcl retrospective missingness}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_retro =         # variable for NA per person
      rowSums(
        is.na(.[pcl.items_retro])
      )
  )

coping.glad.pcl.raw.id %>%
  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
```

@@
